The CrypTool Script: \\ Cryptography, Mathematics and More \\ \vspace{30pt} {\large Background reading\\%*[-8pt] for the free eLearning program CrypTool\\ (10th edition -- distributed with CrypTool version 1.4.30)} \vspace{60pt}

### 2009-07-06 script/en/chapters/primes.tex
fixed error in language en (table placement)

\begin{table}[h]
\begin{center}
\begin{tabular}{|c|cccc|}
\hline    % Eyecatcher_neue-Mersenne
	& {\bf Definition} & {\bf Decimal Digits} & {\bf When} & {\bf Description} \\
\hline
	1  & $2^{43,112,609}-1$ & 12,978,189 & 2008 & Mersenne, 47th known \\
	2  & $2^{42,643,801}-1$ & 12,837,064 & 2009 & Mersenne, 46rd known \\
	3  & $2^{37,156,667}-1$ & 11,185,272 & 2008 & Mersenne, 45nd known \\

>>>>

\begin{table} % don't use [h] (error if table has >24 lines)
\begin{center}
\begin{tabular}{|c|cccc|}
\hline    % Eyecatcher_neue-Mersenne
	& {\bf Definition} & {\bf Decimal Digits} & {\bf When} & {\bf Description} \\
\hline
	1  & $2^{43,112,609}-1$ & 12,978,189 & 2008 & Mersenne, 47th known \\
	2  & $2^{42,643,801}-1$ & 12,837,064 & 2009 & Mersenne, 46th known \\
	3  & $2^{37,156,667}-1$ & 11,185,272 & 2008 & Mersenne, 45th known \\
